Signatures and Induction Principles for Higher Inductive-Inductive Types

### 2019-08-14 paper.tex
add numbering to operations

\begin{alignat*}{5}
  & \Con && : \Set && \text{contexts} \\
  & \Ty  && : \Con\ra\Set && \text{types} \\
  & \Sub  && : \Con\ra\Con\ra\Set && \text{substitutions} \\
  & \Tm  && : (\Gamma:\Con)\ra\Ty\,\Gamma\ra\Set \hspace{2em} && \text{terms} \\
  & \cdot && : \Con && \text{empty context} \\
  & \blank\rhd\blank && : (\Gamma:\Con)\ra\Ty\,\Gamma\ra\Con && \text{context extension} \\
  & \blank[\blank] && : \Ty\,\Delta\ra\Sub\,\Gamma\,\Delta\ra\Ty\,\Gamma && \text{type substitution} \\
  & \id && : \Sub\,\Gamma\,\Gamma && \text{identity substitution} \\
  & [\id] && : A[\id] = A && \text{action of}\,\,\id\,\,\text{on types}\\
  & \blank\circ\blank && : \Sub\,\Theta\,\Delta\ra\Sub\,\Gamma\,\Theta\ra\Sub\,\Gamma\,\Delta && \text{substitution composition} \\
  & \blank[\blank] && : \Tm\,\Delta\,A\ra(\sigma:\Sub\,\Gamma\,\Delta)\ra\Tm\,\Gamma\,(A[\sigma])\hspace{1em} && \text{term substitution} \\
  & ... && \\
  & \U && : \Ty\,\Gamma && \text{universe} \\
  & {\U[]} && : \U[\sigma] = \U && \text{substituting the universe} \\
  & \El && : \Tm\,\Gamma\,\U \ra \Ty\,\Gamma && \text{decoding} \\
  & \Pi && : (A:\Ty\,\Gamma)\ra\Ty\,(\Gamma\rhd A)\ra\Ty\,\Gamma && \text{functions} \\
  & ... &&
\end{alignat*}

@@

\begingroup
\allowdisplaybreaks
\begin{alignat*}{5}
  & \boldsymbol{\cdot}^\A && :\equiv \hat{\top} \\
  & (\Delta,x:A)^\A && :\equiv \hat{(}\hat{\gamma}\in\Delta^\A\hat{)}\timesh A^\A\,\hat{\gamma} \\
  & x^\A\,\hat{\gamma} && :\equiv x^{\text{th}}\text{ component in } \hat{\gamma} \\
  & \U^\A\,\hat{\gamma} && :\equiv \Type_{\hat{0}} \\
  & (\underline{a})^\A\,\hat{\gamma} && :\equiv a^\A\,\hat{\gamma} \\
  & ((x:a)\ra B)^\A\,\hat{\gamma} && :\equiv \hat{(}\hat{x}\in a^\A\,\hat{\gamma}\hat{)}\rah  B^\A\,\hat{(}\hat{\gamma}\commah\hat{x}\hat{)} \\
  & (t\,u)^\A\,\hat{\gamma} && :\equiv \hat{(}t^\A\,\hat{\gamma}\hat{)}\,\hat{(}u^\A\,\hat{\gamma}\hat{)} \\
  & (t=_a u)^\A\,\hat{\gamma} && :\equiv t^\A\,\hat{\gamma} \eqh u^\A\,\hat{\gamma} \\
  & (\refl_t)^\S\,\hat{\gamma} && :\equiv \hat{\refl} \\
  & (\J_{a\,t\,(x.z.p)}\,pr\,_u\,eq)^\A\,\hat{\gamma} && :\equiv \hat{\J}_{\hat{(}a^\A\,\hat{\gamma}\hat{)}\,\hat{(}t^\A\,\hat{\gamma}\hat{)}\,\hat{(}\hat{\lambda} \hat{x}\,\hat{z}.p^\A\,\hat{(}\hat{\gamma}\commah\hat{x}\commah\hat{z}\hat{)}\hat{)}}\,\hat{(}pr^\A\,\hat{\gamma}\hat{)}\,_{\hat{(}u^\A\,\hat{\gamma}\hat{)}}\,\hat{(}eq^\A\,\hat{\gamma}\hat{)} \\
  & (\J\beta_{a\,t\,(x.z.p)}\,pr)^\A\,\hat{\gamma} && :\equiv \hat{\refl} \\
  & (a=_\U b)^\A\,\hat{\gamma} && :\equiv a^\A\,\hat{\gamma} \eqh b^\A\,\hat{\gamma} \\
  & (\refl_a)^\A\,\hat{\gamma} && :\equiv \hat{\refl} \\
  & (\J_{a\,(x.z.p)}\,pr\,_b\,eq)^\A\,\hat{\gamma} && :\equiv \hat{\J}_{\Type_{\hat{0}}\,\hat{(}a^\A\,\hat{\gamma}\hat{)}\,\hat{(}\hat{\lambda} \hat{x}\,\hat{z}.p^\A\,\hat{(}\hat{\gamma}\commah\hat{x}\commah\hat{z}\hat{)}\hat{)}}\,\hat{(}pr^\A\,\hat{\gamma}\hat{)}\,_{\hat{(}b^\A\,\hat{\gamma}\hat{)}}\,\hat{(}eq^\A\,\hat{\gamma}\hat{)} \\
  & (\J\beta_{a\,(x.z.p)}\,pr)^\A\,\hat{\gamma} && :\equiv \hat{\refl} \\
  & ((\hat{x}\in \hat{A})\ra B)^\A\,\hat{\gamma} && :\equiv \hat{(}\hat{x}\in \hat{A}\hat{)}\rah  B^\A\,\hat{\gamma} \\
  & (t\,\hat{u})^\A\,\hat{\gamma} && :\equiv \hat{(}t^\A\,\hat{\gamma}\hat{)}\,\hat{u} \\
  & ((\hat{x}\in \hat{A})\ra b)^\A\,\hat{\gamma} && :\equiv \hat{(}\hat{x}\in \hat{A}\hat{)}\rah  b^\A\,\hat{\gamma} \\
  & (t\,\hat{u})^\A\,\hat{\gamma} && :\equiv \hat{(}t^\A\,\hat{\gamma}\hat{)}\,\hat{u}
\end{alignat*}
\endgroup

@@

\[
\infer{\hat{\Gamma}\vdashh t^\D \in \hat{(}\hat{\gamma}\in\Delta^\A\hat{)}\hat{(}\hat{\gamma^D}\in\Delta^\D\,\hat{\gamma}\hat{)}\rah  A^\D\,\hat{\gamma}\,\hat{\gamma^D}\,\hat{(}t^\A\,\hat{\gamma}\hat{)}}{\hat{\Gamma}\semicol\Delta\vdash t : A}
\]
The implementation of $\blank^\D$ is given below. We leave
$\hat{\gamma}$-s mostly implicit, marking only $\hat{\gamma^D}$ witnesses.
\begingroup
\allowdisplaybreaks
\begin{alignat*}{5}
  & \boldsymbol{\cdot}^\D\,\hat{\gamma} && :\equiv \hat{\top} \\
  & (\Delta,\,x:A)^\D\,(\hat{\gamma}\commah\,\hat{t}) && :\equiv \hat{(}\hat{\gamma^D}\in\Delta^D\,\hat{\gamma}\hat{)}\timesh A^D\,\hat{\gamma^D}\,\hat{t} \\
  & x^\D\,\hat{\gamma^D} && :\equiv x^{\text{th}}\text{ component in } \hat{\gamma^D} \\
  & \U^\D\,\hat{\gamma^D}\,\hat{A} && :\equiv \hat{A} \rah  \Type_{\hat{i}} \\
  & (\underline{a})^\D\,\hat{\gamma^D}\,\hat{t} && :\equiv a^\D\,\hat{\gamma^D}\,\hat{t} \\
  & ((x:a)\ra B)^\D\,\hat{\gamma^D}\,\hat{f} && :\equiv \hat{(}\hat{x}\in a^\A\,\hat{\gamma}\hat{)}\hat{(}\hat{x^D}\in a^\D\,\hat{\gamma^D}\,\hat{x}\hat{)} \rah  B^\D\,\hat{(}\hat{\gamma}\commah\hat{x}\hat{)}\,\hat{(}\hat{\gamma^D}\commah\hat{x^D}\hat{)}\,\hat{(}\hat{f}\,\hat{x}\hat{)} \\
  & (t\,u)^\D\,\hat{\gamma^D} && :\equiv \hat{(}t^\D\,\hat{\gamma^D}\hat{)}\,\hat{(} u^\A\,\hat{\gamma}\hat{)}\,\hat{(}u^\D\,\hat{\gamma^D}\hat{)} \\
  & (t=_a u)^\D\,\hat{\gamma^D}\,\hat{e} && :\equiv \TR_{\hat{(}a^\D\,\hat{\gamma^D}\hat{)}}\,\hat{e}\,\hat{(}t^\D\,\hat{\gamma^D}\hat{)} \eqh u^\D\hat{\gamma^D} \\
  & (\refl_t)^\D\,\hat{\gamma^D} && :\equiv \hat{\refl}_{\hat{(}t^\D\,\hat{\gamma^D}\hat{)}} \\
  & (\J_{a\,t\,(x.z.p)}\,pr\,_u\,eq)^\D\,\hat{\gamma^D} && :\equiv \hat{\J}\,\hat{\big(}\hat{\J}\,\hat{(}pr^\D\,\hat{\gamma^D}\hat{)}\,\hat{(}eq^\A\,\hat{\gamma}\hat{)}\hat{\big)}\,\hat{(}eq^\D\,\hat{\gamma^D}\hat{)} \\
  & (\J\beta_{a\,t\,(x.z.p)}\,pr)^\D\,\hat{\gamma^D} && :\equiv \hat{\refl} \\
  & (a=_\U b)^\D\,\hat{\gamma^D}\,\hat{e} && :\equiv \TR_{\hat{(\lambda A.A\ra\Type_0)}}\,\hat{e}\,\hat{(}a^\D\,\hat{\gamma^D}\hat{)} \eqh b^\D\hat{\gamma^D} \\
  & (\refl_a)^\D\,\hat{\gamma^D} && :\equiv \hat{\refl}_{\hat{(}a^\D\,\hat{\gamma^D}\hat{)}} \\
  & (\J_{a\,(x.z.p)}\,pr\,_b\,eq)^\D\,\hat{\gamma^D} && :\equiv \hat{\J}\,\hat{\big(}\hat{\J}\,\hat{(}pr^\D\,\hat{\gamma^D}\hat{)}\,\hat{(}eq^\A\,\hat{\gamma}\hat{)}\hat{\big)}\,\hat{(}eq^\D\,\hat{\gamma^D}\hat{)} \\
  & (\J\beta_{a\,t\,(x.z.p)}\,pr)^\D\,\hat{\gamma^D} && :\equiv \hat{\refl} \\
  & ((\hat{x}\in \hat{A})\ra B)^\D\,\hat{\gamma^D}\,\hat{f} && :\equiv \hat{(}\hat{x}\in \hat{A}\hat{)}\rah  B^\D\,\hat{\gamma^D}\,\hat{(}\hat{f}\,\hat{x}\hat{)} \\
  & (t\,\hat{u})^\D\,\hat{\gamma^D} && :\equiv t^\D\,\hat{\gamma^D}\,\hat{u} \\
  & ((\hat{x}\in \hat{A})\ra b)^\D\,\hat{\gamma^D}\,\hat{f} && :\equiv \hat{(}\hat{x}\in \hat{A}\hat{)}\rah  b^D\,\hat{\gamma^D}\,\hat{(}\hat{f}\,\hat{x}\hat{)} \\
  & (t\,\hat{u})^\D\,\hat{\gamma^D} && :\equiv t^\D\,\hat{\gamma^D}\,\hat{u}
\end{alignat*}
\endgroup
The predicate for a context is given by iterating $\blank^\D$ for its
constituent types. For a variable, the corresponding witness is looked up from
$\hat{\gamma^D}$.

@@

\begingroup
\allowdisplaybreaks
\begin{alignat*}{5}
  & \boldsymbol{\cdot}^\M\hat{\gamma_0\,\gamma_1} && :\equiv \hat{\top} \\
  & (\Delta,x:A)^\M\,\hat{(\gamma_0,\alpha_0)\,(\gamma_1,\alpha_1)} && :\equiv \hat{(\gamma^M : \blc{\Delta^\M}\,\gamma_0\,\gamma_1)\times \blc{A^\M}\,\gamma_0\,\gamma_1\,\gamma^M\,\alpha_0\,\alpha_1} \\
  & x^\M\,\hat{\gamma_0\,\gamma_1\,\gamma^M} && :\equiv x^{\text{th}}\text{ component in } \hat{\gamma^M} \\
  & \U^\M\,\hat{\gamma_0\,\gamma_1\,\gamma^M\,A_0\,A_1} && :\equiv \hat{A_0\ra A_1 \ra \Type_0} \\
  & (\underline{a})^\M\,\hat{\gamma_0\,\gamma_1\,\gamma^M\,t_0\,\,t_1} && :\equiv \hat{
    \blc{a^\M}\,\gamma_0\,\gamma_1\,\gamma^M\,t_0\,\,t_1}\\
  & ((x:a)\ra B)^\M\,\hat{\gamma_0\,\gamma_1\,\gamma^M\,f_0\,f_1} && :\equiv
  \hat{(x_0 : \blc{(\underline{a})^\A}\,\gamma_0)(x_1 : \blc{(\underline{a})^\A}\,\gamma_1)(x^M : \blc{(\underline{a})^\M}\,\gamma_0\,\gamma_1\,\gamma^M)}\\
  & && \hat{\hspace{1em}\ra \blc{B^\M}\,(\gamma_0,\,x_0)\,(\gamma_1,\,x_1)\,(\gamma^M,\,x^M)\,(f_0\,x_0)\,(f_1\,x_1)}
\end{alignat*}
\endgroup

>>>>

\begin{alignat*}{5}
  & \Con && : \Set && \text{contexts} \\
  & \Ty  && : \Con\ra\Set && \text{types} \\
  & \Sub  && : \Con\ra\Con\ra\Set && \text{substitutions} \\
  & \Tm  && : (\Gamma:\Con)\ra\Ty\,\Gamma\ra\Set \hspace{2em} && \text{terms} \\
  & \cdot && : \Con && \text{empty context} \\
  & \blank\rhd\blank && : (\Gamma:\Con)\ra\Ty\,\Gamma\ra\Con && \text{context extension} \\
  & \blank[\blank] && : \Ty\,\Delta\ra\Sub\,\Gamma\,\Delta\ra\Ty\,\Gamma && \text{type substitution} \\
  & \id && : \Sub\,\Gamma\,\Gamma && \text{identity substitution} \\
  & [\id] && : A[\id] = A && \text{action of}\,\,\id\,\,\text{on types}\\
  & \blank\circ\blank && : \Sub\,\Theta\,\Delta\ra\Sub\,\Gamma\,\Theta\ra\Sub\,\Gamma\,\Delta && \text{substitution composition} \\
  & \blank[\blank] && : \Tm\,\Delta\,A\ra(\sigma:\Sub\,\Gamma\,\Delta)\ra\Tm\,\Gamma\,(A[\sigma])\hspace{1em} && \text{term substitution} \\
  & ... && \\
  & \U && : \Ty\,\Gamma && \text{universe} \\
  & {\U[]} && : \U[\sigma] = \U && \text{substituting the universe} \\
  & \El && : \Tm\,\Gamma\,\U \ra \Ty\,\Gamma && \text{decoding} \\
  & ... && \\
  & \Pi && : (a:\Tm\,\Gamma\,\U)\ra\Ty\,(\Gamma\rhd \E\,a)\ra\Ty\,\Gamma && \text{functions} \\
  & ... &&
\end{alignat*}

@@

\begingroup
\allowdisplaybreaks
\begin{alignat*}{5}
  & (1)\hspace{1em} && \boldsymbol{\cdot}^\A && :\equiv \hat{\top} \\
  & && (\Delta,x:A)^\A && :\equiv \hat{(}\hat{\gamma}\in\Delta^\A\hat{)}\timesh A^\A\,\hat{\gamma} \\
  & && x^\A\,\hat{\gamma} && :\equiv x^{\text{th}}\text{ component in } \hat{\gamma} \\
  & (2) && \U^\A\,\hat{\gamma} && :\equiv \Type_{\hat{0}} \\
  & && (\underline{a})^\A\,\hat{\gamma} && :\equiv a^\A\,\hat{\gamma} \\
  & (3) && ((x:a)\ra B)^\A\,\hat{\gamma} && :\equiv \hat{(}\hat{x}\in a^\A\,\hat{\gamma}\hat{)}\rah  B^\A\,\hat{(}\hat{\gamma}\commah\hat{x}\hat{)} \\
  & && (t\,u)^\A\,\hat{\gamma} && :\equiv \hat{(}t^\A\,\hat{\gamma}\hat{)}\,\hat{(}u^\A\,\hat{\gamma}\hat{)} \\
  & (4) && (t=_a u)^\A\,\hat{\gamma} && :\equiv t^\A\,\hat{\gamma} \eqh u^\A\,\hat{\gamma} \\
  & && (\refl_t)^\S\,\hat{\gamma} && :\equiv \hat{\refl} \\
  & && (\J_{a\,t\,(x.z.p)}\,pr\,_u\,eq)^\A\,\hat{\gamma} && :\equiv \hat{\J}_{\hat{(}a^\A\,\hat{\gamma}\hat{)}\,\hat{(}t^\A\,\hat{\gamma}\hat{)}\,\hat{(}\hat{\lambda} \hat{x}\,\hat{z}.p^\A\,\hat{(}\hat{\gamma}\commah\hat{x}\commah\hat{z}\hat{)}\hat{)}}\,\hat{(}pr^\A\,\hat{\gamma}\hat{)}\,_{\hat{(}u^\A\,\hat{\gamma}\hat{)}}\,\hat{(}eq^\A\,\hat{\gamma}\hat{)} \\
  & && (\J\beta_{a\,t\,(x.z.p)}\,pr)^\A\,\hat{\gamma} && :\equiv \hat{\refl} \\
  & (5) && (a=_\U b)^\A\,\hat{\gamma} && :\equiv a^\A\,\hat{\gamma} \eqh b^\A\,\hat{\gamma} \\
  & && (\refl_a)^\A\,\hat{\gamma} && :\equiv \hat{\refl} \\
  & && (\J_{a\,(x.z.p)}\,pr\,_b\,eq)^\A\,\hat{\gamma} && :\equiv \hat{\J}_{\Type_{\hat{0}}\,\hat{(}a^\A\,\hat{\gamma}\hat{)}\,\hat{(}\hat{\lambda} \hat{x}\,\hat{z}.p^\A\,\hat{(}\hat{\gamma}\commah\hat{x}\commah\hat{z}\hat{)}\hat{)}}\,\hat{(}pr^\A\,\hat{\gamma}\hat{)}\,_{\hat{(}b^\A\,\hat{\gamma}\hat{)}}\,\hat{(}eq^\A\,\hat{\gamma}\hat{)} \\
  & && (\J\beta_{a\,(x.z.p)}\,pr)^\A\,\hat{\gamma} && :\equiv \hat{\refl} \\
  & (6) && ((\hat{x}\in \hat{A})\ra B)^\A\,\hat{\gamma} && :\equiv \hat{(}\hat{x}\in \hat{A}\hat{)}\rah  B^\A\,\hat{\gamma} \\
  & && (t\,\hat{u})^\A\,\hat{\gamma} && :\equiv \hat{(}t^\A\,\hat{\gamma}\hat{)}\,\hat{u} \\
  & (7) && ((\hat{x}\in \hat{A})\ra b)^\A\,\hat{\gamma} && :\equiv \hat{(}\hat{x}\in \hat{A}\hat{)}\rah  b^\A\,\hat{\gamma} \\
  & && (t\,\hat{u})^\A\,\hat{\gamma} && :\equiv \hat{(}t^\A\,\hat{\gamma}\hat{)}\,\hat{u}
\end{alignat*}
\endgroup

@@

\[
\infer{\hat{\Gamma}\vdashh t^\D \in \hat{(}\hat{\gamma}\in\Delta^\A\hat{)}\hat{(}\hat{\gamma^D}\in\Delta^\D\,\hat{\gamma}\hat{)}\rah  A^\D\,\hat{\gamma}\,\hat{\gamma^D}\,\hat{(}t^\A\,\hat{\gamma}\hat{)}}{\hat{\Gamma}\semicol\Delta\vdash t : A}
\]
The implementation of $\blank^\D$ is given below. We leave
$\hat{\gamma}$-s mostly implicit, marking only $\hat{\gamma^D}$ witnesses.
\begingroup
\allowdisplaybreaks
\begin{alignat*}{5}
  & (1)\hspace{1em} && \boldsymbol{\cdot}^\D\,\hat{\gamma} && :\equiv \hat{\top} \\
  & && (\Delta,\,x:A)^\D\,(\hat{\gamma}\commah\,\hat{t}) && :\equiv \hat{(}\hat{\gamma^D}\in\Delta^D\,\hat{\gamma}\hat{)}\timesh A^D\,\hat{\gamma^D}\,\hat{t} \\
  & && x^\D\,\hat{\gamma^D} && :\equiv x^{\text{th}}\text{ component in } \hat{\gamma^D} \\
  & (2) && \U^\D\,\hat{\gamma^D}\,\hat{A} && :\equiv \hat{A} \rah  \Type_{\hat{i}} \\
  & && (\underline{a})^\D\,\hat{\gamma^D}\,\hat{t} && :\equiv a^\D\,\hat{\gamma^D}\,\hat{t} \\
  & (3) && ((x:a)\ra B)^\D\,\hat{\gamma^D}\,\hat{f} && :\equiv \hat{(}\hat{x}\in a^\A\,\hat{\gamma}\hat{)}\hat{(}\hat{x^D}\in a^\D\,\hat{\gamma^D}\,\hat{x}\hat{)} \rah  B^\D\,\hat{(}\hat{\gamma}\commah\hat{x}\hat{)}\,\hat{(}\hat{\gamma^D}\commah\hat{x^D}\hat{)}\,\hat{(}\hat{f}\,\hat{x}\hat{)} \\
  & && (t\,u)^\D\,\hat{\gamma^D} && :\equiv \hat{(}t^\D\,\hat{\gamma^D}\hat{)}\,\hat{(} u^\A\,\hat{\gamma}\hat{)}\,\hat{(}u^\D\,\hat{\gamma^D}\hat{)} \\
  & (4) && (t=_a u)^\D\,\hat{\gamma^D}\,\hat{e} && :\equiv \TR_{\hat{(}a^\D\,\hat{\gamma^D}\hat{)}}\,\hat{e}\,\hat{(}t^\D\,\hat{\gamma^D}\hat{)} \eqh u^\D\hat{\gamma^D} \\
  & && (\refl_t)^\D\,\hat{\gamma^D} && :\equiv \hat{\refl}_{\hat{(}t^\D\,\hat{\gamma^D}\hat{)}} \\
  & && (\J_{a\,t\,(x.z.p)}\,pr\,_u\,eq)^\D\,\hat{\gamma^D} && :\equiv \hat{\J}\,\hat{\big(}\hat{\J}\,\hat{(}pr^\D\,\hat{\gamma^D}\hat{)}\,\hat{(}eq^\A\,\hat{\gamma}\hat{)}\hat{\big)}\,\hat{(}eq^\D\,\hat{\gamma^D}\hat{)} \\
  & && (\J\beta_{a\,t\,(x.z.p)}\,pr)^\D\,\hat{\gamma^D} && :\equiv \hat{\refl} \\
  & (5) && (a=_\U b)^\D\,\hat{\gamma^D}\,\hat{e} && :\equiv \TR_{\hat{(\lambda A.A\ra\Type_0)}}\,\hat{e}\,\hat{(}a^\D\,\hat{\gamma^D}\hat{)} \eqh b^\D\hat{\gamma^D} \\
  & && (\refl_a)^\D\,\hat{\gamma^D} && :\equiv \hat{\refl}_{\hat{(}a^\D\,\hat{\gamma^D}\hat{)}} \\
  & && (\J_{a\,(x.z.p)}\,pr\,_b\,eq)^\D\,\hat{\gamma^D} && :\equiv \hat{\J}\,\hat{\big(}\hat{\J}\,\hat{(}pr^\D\,\hat{\gamma^D}\hat{)}\,\hat{(}eq^\A\,\hat{\gamma}\hat{)}\hat{\big)}\,\hat{(}eq^\D\,\hat{\gamma^D}\hat{)} \\
  & && (\J\beta_{a\,t\,(x.z.p)}\,pr)^\D\,\hat{\gamma^D} && :\equiv \hat{\refl} \\
  & (6) && ((\hat{x}\in \hat{A})\ra B)^\D\,\hat{\gamma^D}\,\hat{f} && :\equiv \hat{(}\hat{x}\in \hat{A}\hat{)}\rah  B^\D\,\hat{\gamma^D}\,\hat{(}\hat{f}\,\hat{x}\hat{)} \\
  & && (t\,\hat{u})^\D\,\hat{\gamma^D} && :\equiv t^\D\,\hat{\gamma^D}\,\hat{u} \\
  & (7) && ((\hat{x}\in \hat{A})\ra b)^\D\,\hat{\gamma^D}\,\hat{f} && :\equiv \hat{(}\hat{x}\in \hat{A}\hat{)}\rah  b^D\,\hat{\gamma^D}\,\hat{(}\hat{f}\,\hat{x}\hat{)} \\
  & && (t\,\hat{u})^\D\,\hat{\gamma^D} && :\equiv t^\D\,\hat{\gamma^D}\,\hat{u}
\end{alignat*}
\endgroup
The predicate for a context is given by iterating $\blank^\D$ for its
constituent types. For a variable, the corresponding witness is looked up from
$\hat{\gamma^D}$.

@@

\begingroup
\allowdisplaybreaks
\begin{alignat*}{5}
  & (1)\hspace{1em} && \boldsymbol{\cdot}^\M\hat{\gamma_0\,\gamma_1} && :\equiv \hat{\top} \\
  & && (\Delta,x:A)^\M\,\hat{(\gamma_0,\alpha_0)\,(\gamma_1,\alpha_1)} && :\equiv \hat{(\gamma^M : \blc{\Delta^\M}\,\gamma_0\,\gamma_1)\times \blc{A^\M}\,\gamma_0\,\gamma_1\,\gamma^M\,\alpha_0\,\alpha_1} \\
  & && x^\M\,\hat{\gamma_0\,\gamma_1\,\gamma^M} && :\equiv x^{\text{th}}\text{ component in } \hat{\gamma^M} \\
  & (2) && \U^\M\,\hat{\gamma_0\,\gamma_1\,\gamma^M\,A_0\,A_1} && :\equiv \hat{A_0\ra A_1 \ra \Type_0} \\
  & && (\underline{a})^\M\,\hat{\gamma_0\,\gamma_1\,\gamma^M\,t_0\,\,t_1} && :\equiv \hat{
    \blc{a^\M}\,\gamma_0\,\gamma_1\,\gamma^M\,t_0\,\,t_1}\\
  & (3) && ((x:a)\ra B)^\M\,\hat{\gamma_0\,\gamma_1\,\gamma^M\,f_0\,f_1} && :\equiv
  \hat{(x_0 : \blc{(\underline{a})^\A}\,\gamma_0)(x_1 : \blc{(\underline{a})^\A}\,\gamma_1)(x^M : \blc{(\underline{a})^\M}\,\gamma_0\,\gamma_1\,\gamma^M)}\\
  & && && \hat{\hspace{1.7em}\ra \blc{B^\M}\,(\gamma_0,\,x_0)\,(\gamma_1,\,x_1)\,(\gamma^M,\,x^M)\,(f_0\,x_0)\,(f_1\,x_1)}
\end{alignat*}
\endgroup
